% EDUCATION ########################################################################
\cvsection{Education}
\cvevent{3rd Year Bachelor of Computer Science (BCS)}{University of British Columbia, GPA: 4.3/4.3}{\medskip September 2022 -- May 2025}{}
\divider\small
\cvevent{BSc. Environmental and Conservation Sciences in Conservation Biology}{University of Alberta, GPA: 3.7/4.0}{\medskip September 2017 -- May 2022}{}
% \divider

% SKILLS/COURSEWORK ##############################################################



% EXTRACURRICULARS ##################################################################
\cvsection{Projects}
\cvevent{\href{https://github.com/MeganSorenson/BCS-Hackathon-2023}{2nd Place: ChatGPT Youtube Video Q\&A Chrome Extension [GitHub]}}{}{March 2023}{}
\begin{itemize}
  % Created a python library that acts as an API for a CLI interface. This is also importable to be used within python scripts.
  \item Utilized the OpenAI API and YouTube API to summarize and provide Q\&A functionality for any YouTube video with available captions.
  \item Lead the creation of the backend server and aided in integrating the Chrome Extension's UI into YouTube's video-play bar.
  \item \underline{\textit{Utilized:}} Python, JavaScript, ChatGPT, Flask, Chrome Extensions
\end{itemize}
\divider\small

\cvevent{\href{https://github.com/MeganSorenson/Beeno}{Parking Airbnb: NwHacks 2023 Project [GitHub]}}{}{January 2023}{}
\begin{itemize}
  % Created a python library that acts as an API for a CLI interface. This is also importable to be used within python scripts.
  \item Created a web application that allows users to post and book parking spaces and manage their stalls and bookings.
  \item Lead the creation of the database and backend server using sqlite and Flask, and helped the frontend team integrate our API into their code.
  \item \underline{\textit{Utilized:}} Python, Flask, JavaScript, CSS, HTML, full stack 
\end{itemize}
\divider\small

\cvevent{\href{https://github.com/MeganSorenson/WorldOfWordle}{World Of Wordle Java Application [GitHub]}}{}{September 2022 - December 2022}{}
\begin{itemize}
  % Created a python library that acts as an API for a CLI interface. This is also importable to be used within python scripts.
  \item Created a wordle-inspired Java application with extended options to play simultaneously with one, two, or three boards.
  \item Utilized Java Swing to create a GUI where guesses are color populated based on their accuracy and included serialization of game state to allow time-interupted playing.
  \item Created a unit testing suite with 100 percent code coverage.
  \item \underline{\textit{Utilized:}} Java, JUnit, json Serialization, Event Logging, Software Construction
\end{itemize}





